---
title: "Analysis and Graph Generation"
author: "Tan Kia Leng"
date: "2023-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(afex)
library(emmeans)
```


## Reading in dataset
```{r}
## Converting data source from sav to csv
# haven::read_sav("raw/Dataset (1).sav") %>% 
#   write.csv("data/data_raw (from sav).csv",row.names=FALSE)

data <- read_csv("data/data_raw (from sav).csv")
```

## Data Cleaning, selection of variables
Use ends_with to select variables of concern.

Note: Columns where conditions are NA are removed.
- Should print information in output

```{r}
vars_of_interest <- c("success","stress","opt","RFS_pro","RFS_pre")
select_vars <- function(data,vars_of_interest) {
  suffix <- paste0("[0-9]_",vars_of_interest,"$")
  selected <- data %>% 
    select(ID, Condition, matches(suffix)) 
  return(selected)
}

data_req <- select_vars(data,vars_of_interest = vars_of_interest)

```


## Time Manipulation
Output: One row represents each level of Intervention-Time for each individual, in tidy format
e.g. Promotion-S3-Individual-1 in each role

```{r}

rename_cols <- function(data) {
  data %>% rename("Success" = "success",
           "Stress" = "stress",
           "Optimism" = "opt",
           "RFS_Promotion" = "RFS_pro",
           "RFS_Prevention" = "RFS_pre",
           "Intervention" = "Condition") 
}

current_period <- function(data) {
  data %>% 
    pivot_longer(cols= matches(vars_of_interest),
                 names_to=c("Time","Var"),values_to=c("Value"),
                 names_pattern=('(S[1-9])_(.*)')) %>% 
    pivot_wider(names_from = Var, values_from = Value) %>% rename_cols()  %>% 
  
    mutate(Intervention_Pro = ifelse(str_detect(Intervention,c("Promotion|Combined")),1,0),
         Intervention_Pre = ifelse(str_detect(Intervention,c("Prevention|Combined")),1,0),
         .after = "Intervention"
         )
}

data_pred_curr <- current_period(data_req)

predictors <- c("stress","opt","RFS_pre","RFS_pro")
dv <- c("success")


future_pred <- function(data, predictors,dv) {
  data_req %>% 
    # pivot variables longer to have one row rep var-time pair
    pivot_longer(cols= matches(vars_of_interest),
                   names_to=c("Time","Var"),values_to=c("Value"),
                   names_pattern=('(S[1-9])_(.*)')) %>% 
    # drop success at S1 and predicotrs at S5
    mutate(Time = as.numeric(str_extract(Time,"[0-9]")),
           keep = ((Var %in% predictors) &(Time<5))|((Var %in% dv) &(Time>1))) %>% 
    filter(keep == TRUE) %>% 
    mutate(keep = NULL,
           
    # match predictors at previous time to success at curr time
           is_predictor = Var %in% predictors,
           pred_for = case_when(
             is_predictor ~ paste0("S",ifelse(Time+1==2,3,Time+1)),
             TRUE ~ paste0("S",Time)),
           is_predictor=NULL) %>% 
    pivot_wider(values_from=c(Time,Value),names_from = Var) %>% 
    rename_with(~ str_remove(.x,"Value_")) %>% 
    
    rename_cols() %>% 
    mutate(Intervention_Pro = ifelse(str_detect(Intervention,c("Promotion|Combined")),1,0),
           Intervention_Pre = ifelse(str_detect(Intervention,c("Prevention|Combined")),1,0),
           .after = "Intervention"
           )
} 

data_pred_future <- future_pred(data_req,predictors,dv)
```


```{r}
filter_condition <- function(data, conditions_to_keep) {
  data %>% 
    filter(Intervention %in% conditions_to_keep)
}

```


```{r}
data_pred_future %>% 
  select(Intervention,RFS_Promotion,Optimism,RFS_Prevention,Stress,Success)
```

```{r}
data_for_corrs <- data_pred_future %>% 
  select(Intervention_Pro,RFS_Promotion,Optimism,
         Intervention_Pre,RFS_Prevention,Stress,
         Success)
correlations <- cor(data_for_corrs,use="pairwise.complete.obs")
# write.csv(correlations,file="correlations.csv")
```


## Plot
```{r}
mean_two_sd_optimism <- function(data) {
  mean_opt <- mean(data$Optimism,na.rm=TRUE)
  sd_opt <- sd(data$Optimism,na.rm=TRUE)
  
  return (c("Low"= mean_opt-2*sd_opt,
            "Medium" = mean_opt,
            "High" = mean_opt+2*sd_opt))
}

mean_two_sd_stress <- function(data) {
  mean_stress <- mean(data$Stress,na.rm=TRUE)
  sd_stress <- sd(data$Stress,na.rm=TRUE)
  
  return (c("Low"= mean_stress-2*sd_stress,
            "Medium" = mean_stress,
            "High" = mean_stress+2*sd_stress))
}
```


## ANOVA
```{r}

intv_pro_opt_model <- function(data) {
  print(data)
  lm(Success ~ Intervention*Optimism, data = data)
}

presence_pro_opt_model <- function(data) {
  lm(Success ~ Intervention_Pro*Optimism, data = data)
}

rfs_pro_opt_model <- function(data) {
  lm(Success ~ RFS_Promotion*Optimism, data = data)
}


intv_pre_stress_model <- function(data) {
  print(data)
  lm(Success ~ Intervention*Stress, data = data)
}

presence_pre_stress_model <- function(data) {
  lm(Success ~ Intervention_Pre*Stress, data = data)
}


rfs_pre_stress_model <- function(data) {
  lm(Success ~ RFS_Prevention*Stress, data = data)
}


```

## Correlation of data at the same time point
How do interventions, regulatory focus strategies, optimism and stress level relate to feelings of success at any time points?

Note: purely correlational

Within the same time, feelings of success and optimism levels were measured after 

InterPro x Opt --> Success


### Pro

#### Current
```{r}
data <- data_pred_curr %>% 
  filter_condition(c("Promotion Focus","Control")) %>% 
  filter(Time != "S1")

intv_pro_opt_curr <-intv_pro_opt_model(data)
summary(intv_pro_opt_curr)

emm <- emmeans(intv_pro_opt_curr, ~ Intervention | Optimism,
        at = list(Optimism=mean_two_sd_optimism(data))) 
pairs(emm)

plot_data <- data.frame(
  Intervention = rep(sort(unique(data$Intervention)),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Intervention = factor(Intervention,levels=c("Control","Promotion Focus")),
         Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(intv_pro_opt_curr,plot_data)

ggplot(plot_data) +
  geom_col(aes(x=Intervention,y=Success,fill=Optimism_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Promotion-focused Intervention on Success, \
Moderated by Optimism", 
       x = "Intervention", y = "Success",fill="Optimism") +
  theme_minimal()

```

```{r}
data <- data_pred_curr %>% 
  filter(Time != "S1")

presence_pro_opt_curr <- presence_pro_opt_model(data)
summary(presence_pro_opt_curr)

emm <- emmeans(presence_pro_opt_curr, ~ Intervention_Pro | Optimism,
        at = list(Optimism=mean_two_sd_optimism(data))) 
pairs(emm)

plot_data <- data.frame(
  Intervention_Pro = rep(c(0,1),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(presence_pro_opt_curr,plot_data)
plot_data$Intervention_Pro <- ifelse(plot_data$Intervention_Pro == 0,"Absent","Present")

ggplot(plot_data) +
  geom_col(aes(x=Intervention_Pro,y=Success,fill=Optimism_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Presence of Promotion-focused Intervention on Success,\
Moderated by Optimism", 
       x = "Presence of Promotion-Focused Intervention", y = "Success",fill="Optimism") +
  theme_minimal()

```

```{r}
rfs_pro_opt_curr <- rfs_pro_opt_model(data_pred_curr)
summary(rfs_pro_opt_curr)

plot_data <- data.frame(
  RFS_Promotion = rep(c(1,5),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(rfs_pro_opt_curr,plot_data)


ggplot(plot_data) +
  geom_path(aes(x=RFS_Promotion,y=Success,linetype=Optimism_Level), show.legend=FALSE) +
  geom_text(aes(x=RFS_Promotion,y=Success,label=Optimism_Level), nudge_x = 0.05,hjust=0,
            data = filter(plot_data, RFS_Promotion == 5)) +
  scale_x_continuous(limits = c(1, 5.5)) +
  scale_y_continuous(limits = c(1,5)) +
  labs(title = "Effect of Self-Reported Promotion-Focus Scores on Success, \
Moderated by Optimism", 
       x = "RFSS Promotion Score", y = "Success") +
  theme_minimal()
```

#### Predictions
```{r}
data <- data_pred_future %>% 
  filter_condition(c("Promotion Focus","Control"))
intv_pro_opt_future <- intv_pro_opt_model(data)
summary(intv_pro_opt_future)

emm <- emmeans(intv_pro_opt_future, ~ Intervention | Optimism,
        at = list(Optimism=mean_two_sd_optimism(data))) 
pairs(emm)

plot_data <- data.frame(
  Intervention = rep(sort(unique(data$Intervention)),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Intervention = factor(Intervention,levels=c("Control","Promotion Focus")),
         Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(intv_pro_opt_future,plot_data)

ggplot(plot_data) +
  geom_col(aes(x=Intervention,y=Success,fill=Optimism_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Promotion-focused Intervention on Future Success,\
Moderated by Optimism", 
       x = "Intervention", y = "Success",fill="Optimism") +
  theme_minimal()
```

Promotion-focused intervention increases feelings of success. Increased optimism at previous time point also predicts for increased feelings of success. Optimism decreases feelings of success among individuals who underwent a the promotion-focused intervention.

```{r}

presence_pro_opt_future <- presence_pro_opt_model(data_pred_future)
summary(presence_pro_opt_future)

emm <- emmeans(presence_pro_opt_future, ~ Intervention_Pro | Optimism,
        at = list(Optimism=mean_two_sd_optimism(data_pred_future))) 
pairs(emm)

plot_data <- data.frame(
  Intervention_Pro = rep(c(0,1),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(presence_pro_opt_future,plot_data)
plot_data$Intervention_Pro <- ifelse(plot_data$Intervention_Pro == 0,"Absent","Present")

ggplot(plot_data) +
  geom_col(aes(x=Intervention_Pro,y=Success,fill=Optimism_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Presence of Promotion-focused Intervention on \
Future Success, Moderated by Optimism", 
       x = "Presence of Promotion-Focused Intervention", y = "Success",fill="Optimism") +
  theme_minimal()

```


```{r}
rfs_pro_opt_future <- rfs_pro_opt_model(data_pred_future)
summary(rfs_pro_opt_future)

plot_data <- data.frame(
  RFS_Promotion = rep(c(1,5),each=3),
  Optimism = rep(mean_two_sd_optimism(data),times=2),
  Optimism_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Optimism_Level = factor(Optimism_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(rfs_pro_opt_future,plot_data)


ggplot(plot_data) +
  geom_path(aes(x=RFS_Promotion,y=Success,linetype=Optimism_Level), show.legend=FALSE) +
  geom_text(aes(x=RFS_Promotion,y=Success,label=Optimism_Level), nudge_x = 0.05,hjust=0,
            data = filter(plot_data, RFS_Promotion == 5)) +
  scale_x_continuous(limits = c(1, 5.5)) +
  scale_y_continuous(limits = c(1, 5)) +
  labs(title = "Effect of Self-Reported Promotion-Focus Scores on Future Success, \
Moderated by Optimism", 
       x = "RFSS Promotion Score", y = "Success") +
  theme_minimal()
```

Current states of promotion-focused strategy and optimism do not predict future feelings of success



### Prevention
#### Current
```{r}
data <- data_pred_curr %>% 
  filter_condition(c("Prevention Focus","Control")) %>% 
  filter(Time != "S1")
intv_pre_stress_curr <- intv_pre_stress_model(data)
summary(intv_pre_stress_curr)
emm <- emmeans(intv_pre_stress_curr, ~ Intervention | Stress,
        at = list(Stress=mean_two_sd_stress(data))) 
pairs(emm)

plot_data <- data.frame(
  Intervention = rep(sort(unique(data$Intervention)),each=3),
  Stress = rep(mean_two_sd_optimism(data),times=2),
  Stress_Level = rep(names(mean_two_sd_optimism(data)),times=2)
  ) %>% 
  mutate(Intervention = factor(Intervention,levels=c("Control","Prevention Focus")),
         Stress_Level = factor(Stress_Level,levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(intv_pre_stress_curr,plot_data)

ggplot(plot_data) +
  geom_col(aes(x=Intervention,y=Success,fill=Stress_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Prevention-Focused Intervention on Success,\
Moderated by Stress", 
       x = "Intervention", y = "Success",fill="Stress") +
  theme_minimal()
```

For participants with low stress, Prevention focused interventions decreases feelings of success. However, they increase feelings of success for participants with high stress levels

```{r}
data <- data_pred_curr %>% 
  filter(Time != "S1")

presence_pre_stress_curr <- presence_pre_stress_model(data)
summary(presence_pre_stress_curr)
emm <- emmeans(presence_pre_stress_curr, ~ Intervention_Pre | Stress,
        at = list(Stress=mean_two_sd_stress(data))) 
pairs(emm)


plot_data <- data.frame(
  Intervention_Pre = rep(c(0,1),each=3),
  Stress= rep(mean_two_sd_stress(data),times=2),
  Stress_Level = rep(names(mean_two_sd_stress(data)),times=2)
  ) %>% 
  mutate(Stress_Level = factor(Stress_Level,levels=c("Low","Medium","High")))
                              
plot_data$Success <- predict(presence_pre_stress_curr,plot_data)
plot_data$Intervention_Pre <- ifelse(plot_data$Intervention_Pre == 0,"Absent","Present")

ggplot(plot_data) +
  geom_col(aes(x=Intervention_Pre,y=Success,fill=Stress_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Presence of Prevention-focused Intervention on Success,\
Moderated by Stress", 
       x = "Presence of Prevention-Focused Intervention", y = "Success",fill="Stress") +
  theme_minimal()

```

```{r}
rfs_pre_stress_curr <- rfs_pre_stress_model(data_pred_curr)
summary(rfs_pre_stress_curr)

plot_data <- data.frame(
  RFS_Prevention = rep(c(1,5),each=3),
  Stress = rep(mean_two_sd_stress(data),times=2),
  Stress_Level = rep(names(mean_two_sd_stress(data)),times=2)
  ) %>% 
  mutate(Stress_Level = factor(Stress_Level,
                               labels=c("Low Stress", "Medium Stress", "High Stress"),
                               levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(rfs_pre_stress_curr,plot_data)


ggplot(plot_data) +
  geom_path(aes(x=RFS_Prevention,y=Success,linetype=Stress_Level)) +
  # geom_text(aes(x=RFS_Prevention,y=Success,label=Stress_Level), nudge_x = 0.05,hjust=0,
  #           data = filter(plot_data, RFS_Prevention == 5)) +
  # scale_x_continuous(limits = c(1, 6),breaks = seq(1, 5, by = 1)) +
  scale_y_continuous(limits = c(0, 4)) +
  labs(title = "Effect of Self-Reported Prevention-Focus Scores on Success, \
Moderated by Stress", linetype = "Stress",
       x = "RFSS Prevention Score", y = "Success") +
  theme_minimal()
```

Feelings of success are higher among participants higher among participants who are more stressed. Non significant Stress x RFS_pre interaction


## Prediction

```{r}
data <- data_pred_future %>% 
  filter_condition(c("Prevention Focus","Control"))
intv_pre_stress_future <- intv_pre_stress_model(data)
summary(intv_pre_stress_future)
emm <- emmeans(intv_pre_stress_future, ~ Intervention | Stress,
        at = list(Stress=mean_two_sd_stress(data))) 
pairs(emm)

plot_data <- data.frame(
  Intervention = rep(sort(unique(data$Intervention)),each=3),
  Stress = rep(mean_two_sd_stress(data),times=2),
  Stress_Level = rep(names(mean_two_sd_stress(data)),times=2)
  ) %>% 
  mutate(Intervention = factor(Intervention,levels=c("Control","Prevention Focus")),
         Stress_Level = factor(Stress_Level,levels=c("Low","Medium","High")))
plot_data$Success <- predict(intv_pre_stress_future,plot_data)

ggplot(plot_data) +
  geom_col(aes(x=Intervention,y=Success,fill=Stress_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Prevention-Focused Intervention on Future Success, \
Moderated by Stress", 
       x = "Intervention", y = "Success",fill="Stress") +
  theme_minimal()
```

Prevention-focused intervention decreases feelings of success. Increased stress has no significant effect on feelings of success. Stress increases feelings of success among individuals who underwent the prevention-focused intervention.


```{r}
presence_pre_stress_future <- presence_pre_stress_model(data_pred_future)
summary(presence_pre_stress_future)

library(emmeans)
emm <- emmeans(presence_pre_stress_future, ~ Intervention_Pre | Stress,
        at = list(Stress=mean_two_sd_stress(data_pred_future))) 
pairs(emm)

plot_data <- data.frame(
  Intervention_Pre = rep(c(0,1),each=3),
  Stress = rep(mean_two_sd_stress(data),times=2),
  Stress_Level = rep(names(mean_two_sd_stress(data)),times=2)
  ) %>% 
  mutate(Stress_Level = factor(Stress_Level,levels=c("Low","Medium","High")))

plot_data$Success <-predict(presence_pre_stress_future,plot_data)
plot_data$Intervention_Pre <- ifelse(plot_data$Intervention_Pre == 0,"Absent","Present")

ggplot(plot_data) +
  geom_col(aes(x=Intervention_Pre,y=Success,fill=Stress_Level),position = "dodge") +
  scale_fill_manual(values = c("Low" = "#CCCCCC", "Medium" = "#969696", "High" = "#636363")) +
  labs(title = "Effect of Presence of Prevention-focused Intervention on \
Future Success, Moderated by Stress", 
       x = "Presence of Prevention-Focused Intervention", y = "Success",fill="Stress") +
  theme_minimal()

```


```{r}
rfs_pre_stress_future <- rfs_pre_stress_model(data_pred_future)
summary(rfs_pre_stress_future)

plot_data <- data.frame(
  RFS_Prevention = rep(c(1,5),each=3),
  Stress = rep(mean_two_sd_stress(data),times=2),
  Stress_Level = rep(names(mean_two_sd_stress(data)),times=2)
  ) %>% 
  mutate(Stress_Level = factor(Stress_Level,
                               labels=c("Low Stress", "Medium Stress", "High Stress"),
                               levels=c("Low","Medium","High")))
                              

plot_data$Success <- predict(rfs_pre_stress_future,plot_data)


ggplot(plot_data) +
  geom_path(aes(x=RFS_Prevention,y=Success,linetype=Stress_Level)) +
  # geom_text(aes(x=RFS_Prevention,y=Success,label=Stress_Level), nudge_x = 0.05,  
  #           ,hjust=0,
  #           data = filter(plot_data, RFS_Prevention == 5)) +
  # scale_x_continuous(limits = c(1, 6),breaks = seq(1, 5, by = 1)) +
  scale_y_continuous(limits = c(0, 4)) +
  labs(title = "Effect of Self-Reported Prevention-Focus Scores on Future Success, \
Moderated by Stress", linetype = "Stress",
       x = "RFSS Prevention Score", y = "Success") +
  theme_minimal()
```

Current states of prevention-focused strategy and stress do not predict future feelings of success
